\documentclass{curriculum}
\author{Rolf Vidar {\bfseries Mazunki} Hoksaas}
\email{me@mazunki.tech}
\phone{+4748447243}
\github{@mazunki}
\linkedin{@mazunki}
\website{mazunki.dev}
\jobtitle{Software Engineer}
\date{}

\begin{document}
	\maketitle

	\section{Summary}
	\paragraph{} I'm a curious person and developer by nature, so I will dig into anything in order to understand it. I am an active defendant of open source development, and continuously try to search for things to improve. 
	\paragraph{} I have more than average knowledge about many things, making me a great asset anywhere. I combine pieces of knowledge from different places in order to build greater things. That's why I have so many personal projects going on in my free time.

	\section{Skills}
	\subsection{Languages}
	\begin{half}
		\subsubsection{Programming}
			\begin{itemize}
				\item Python, Java
				\item C/C++, GoLang
				\item sed, awk, Bash, sh, RegEx, POSIX...
			\item Different paragidms: Object Oriented, Functional, Data Structures...
			\end{itemize}
		\subsubsection{Markup}
			\begin{itemize}
				\item \LaTeX
				\item HTML, CSS3
				\item Tkinter, FXML, GTK3
			\end{itemize}
	\end{half}
	\begin{half}
		\subsubsection{Natural languages}
			\begin{itemize}
				\item English --- fluent
				\item Spanish --- native
				\item Norwegian --- native
				\item Catalan --- fluent
				% \item Esperanto --- intermediate
				% \item Japanese --- beginner
			\end{itemize}
	\subsection{Hands on}
	\begin{itemize} 
		\item Decent knowledge about electronics
		\item Project management skills
		\item Teamwork and workflow
	\end{itemize}	

	\end{half}


	\section{Experience}	
	\begin{half}
	\subsection{Work}
		\begin{itemize}
		\item Maritime industry
			\subitem Worked for over 9 years
			\subitem Cargo, passengers, maintenance
		\end{itemize}
	\end{half}
	\begin{half}
	\subsection{Projects}
		\begin{itemize}
			\item TJ Bot --- An AI-based home device which can make your life easier.
			\item A repository with several linux scripts for my own use.
			\item Integrating input devices between different platforms I use.
			\item Currently I spend most of my time enforcing the XDG standard onto my machines
			\item Using a home machine as a server
			\item Actively participating in the FOSS community.
		\end{itemize}
	\end{half}
	\section{Academics}
	\begin{half}
	\subsection{School}
		\begin{itemize}
			\item Philsophy
				\subitem University of Oslo
				\subitem Currently enrolled
			\item Robotics and Intelligent systems
				\subitem University of Oslo
				\subitem Complete Bachelor's by summer
			\item Applied Data Science
				\subitem Noroff University
				\subitem One year
		\end{itemize}
	\subsection{Titles}
		\begin{itemize}
			\item Boat Driver License
			\item Crowd- and Crisis Management
			\item Safety Course for seafarers
		\end{itemize}
	\end{half}
	\begin{half}
	\subsection{Courses}
		\begin{itemize}
			\item Calculus I \& II
			\item Introduction to Computing Technology
			\item Object-Oriented Programming I \& II
			\item Examen Philosophicum
			\item Linear Algebra
			\item Mechatronics
			\item Systems, Requirements and Consequences
			\item Introduction to Applied Statistics
			\item Problem Solving with Abstract-level Languages
			\item Digital Technique and Computer Architecture
			\item Algorithms and Data Structures
			\item Introduction to Operating Systems and Data Communications
			\item Introduction to Philosophy History
			\item Introduction to Epistemology and Philosophy of Science
			\item Introduction to Metaphysics and Philosophy of the Consciousness
		\end{itemize}
	\end{half}

\end{document}
